\addcontentsline{toc}{chapter}{СПИСОК ИСПОЛЬЗОВАННЫХ ИСТОЧНИКОВ}

\renewcommand\bibname{СПИСОК ИСПОЛЬЗОВАННЫХ ИСТОЧНИКОВ}
\begin{thebibliography}{}

\setlength\bibindent{1.25cm}
\makeatletter
\let\old@biblabel\@biblabel
\def\@biblabel#1{\kern\bibindent\old@biblabel{#1}}
\makeatother

\bibitem{google} Google Search Statistics [Электронный ресурс]. --- URL: \url{https://www.internetlivestats.com/google-search-statistics/} (дата обращения: 24.02.2023).

\bibitem{ML_no_wors} Бурков А. Машинное обучение без лишних слов / А. Бурков. --- СПб.: Питер. --- 2020. --- 192 с.

\bibitem{ML_for_rank} Городилов А. Методы машинного обучения для задачи ранжирования / А. Городилов // Труды Третьей Российской конференции молодых ученых по информационному поиску. --- 2009. --- С. 12--20.

\bibitem{ML_for_SE} Борисовская А. А. Применение методов машинного обучения в задачах ранжирования в поисковых информационных системах. / А. А. Борисовская // Информационные технологии в управлении. --- 2021. --- С. 1--13.

\bibitem{LR} Cossock D. Subset ranking using regression / Cossock D., Zhang T.// In Proceedings of the 19th Annual Conference on Learning Theory (COLT). --- 2006. --- P. 605–619.

\bibitem{RankSVM} Herbrich R. Support vector learning for ordinal regression / Herbrich R., Graepel T., Obermayer K. // In International Conference on Artificial Neural Networks. --- 1999. ---
P. 97--102.

\bibitem{LamdaRank} Burges C. J. Learning to rank with nonsmooth cost functions / Burges C. J., Ragno R., Le Q. V. // Advances in Neural Information Processing Systems 19. --- 2007. --- P. 193--200.

\bibitem{ListNet} Z. Cao Learning to rank: From pairwise approach to listwise approach / Z. Cao, T. Qin,T.-Y. Liu et al. // Proceedings of the 24th International Conference on Machine Learning. --- 2007. --- P. 129--136.

\bibitem{LETOR3} Tao Qin LETOR: A Benchmark Collection for Research on
Learning to Rank for Information Retrieval / Tao Qin, Tie-Yan Liu, Jun Xu et el. // Information Retrieval. --- 2010. --- P. 346--374.

\bibitem{AOL} Antonino Freno Learning to Rank Using Markov Random Fields / Antonino Freno, Tiziano Papini, Michelangelo Diligenti // 2011 10th International Conference on Machine Learning and Applications and Workshops. --- 2011. --- P. 257--262.

\bibitem{Yahoo} Olivier Chapelle Yahoo! Learning to Rank Challenge Overview / Olivier Chapelle, Yi Chang  // Proceedings of the learning to rank challenge. --- 2011. --- P. 1--24.

\bibitem{WCL2R} Otavio D. A. Alcantara WCL2R: a benchmark collection for learning to rank research with clickthrough data / Otavio D. A. Alcantara, Alvaro R. Pereira Jr., Humberto M. de Almeida // Journal of Information and Data Management. – 2010. --- P. 551--551.

\bibitem{MSLR} Microsoft Learning to Rank Datasets [Электронный ресурс]. --- URL: \url{https://www.microsoft.com/en-us/research/project/mslr/} (дата обращения: 05.03.2023)

\bibitem{istella} LETOR Dataset [Электронный ресурс]. --- URL: \url{https://istella.ai/data/letor-dataset/} (дата обращения: 05.03.2023)

\bibitem{metrics} Беляков А.В Метрики качества в задачах ранжирования информации / Беляков А.В // Информационные технологии, межвузовский сборник научных трудов. --- Рязань: Рязанский государственный радиотехнический университет имени В.Ф. Уткина. --- 2019. --- C. 36--39.

\bibitem{LRM2} Chieh-Jen Wang Automatic Construction of An Evaluation Dataset from Wisdom of the Crowds for Information Retrieval Applications / Chieh--Jen Wang, Hung-Sheng Huang, Hsin-Hsi Chen // 2012 IEEE International Conference on Systems. – 2012. --- P. 490--495.

\bibitem{LRM3} Maksims N. Volkovs Loss-sensitive Training of Probabilistic Conditional Random Fields / Chieh--Jen Wang, Hung-Sheng Huang, Hsin-Hsi Chen // arXiv preprint arXiv:1107.1805. – 2011.

\bibitem{RSVMM1} Robert Busa-Fekete Tune and mix: Learning to rank using ensembles of calibrated multi-class classifiers / Robert Busa-Fekete, Balazs Kegl, Tamas Elteto et al. // Machine Learning. – 2013. --- P. 261--292.

\bibitem{RSVMM2} Tiziano Papini Learning-to-rank with Prior Knowledge as Global Constraints / Tiziano Papini, Michelangelo Diligenti // WORKSHOP ON COMBINING. – 2012. --- P. 35--40.

\bibitem{LDRM1} Xinyi Dai U-rank: Utility-oriented Learning to Rank with Implicit Feedback / Xinyi Dai, Jiawei Hou, Qing Liu et al. // Proceedings of the 29th ACM international conference on information and knowledge management. – 2020. --- P. 2373--2380.

\bibitem{LDRM2} Ming Tan Direct Optimization of Ranking Measures for Learning to Rank Models / Ming Tan, Tian Xia, Lily Guo et al. // Proceedings of the 19th ACM SIGKDD international conference on Knowledge discovery and data mining. – 2013. --- P. 856--864.

\bibitem{LNM1} Hai-Tao Yu PT-Ranking: A Benchmarking Platform for Neural Learning-to-Rank / Ming Tan, Tian Xia, Lily Guo et al. // arXiv preprint arXiv:2008.13368. – 2020. --- P. 856--864.

\bibitem{cmp} Niek Tax A Cross-Benchmark Comparison of 87 Learning to Rank Methods / Niek Tax, Sander Bockting, Djoerd Hiemstra // Information Processing and Management. ---2015. --- P. 757--772.

\end{thebibliography}


